Arrows for Parallel Computations

### 2017-08-23 paper/content/benchmarks.tex
reordering code in benchmarks.tex for easier reading

\newcommand{\rmtest}{Rabin--Miller test\xspace}
\newcommand{\sudokutest}{Sudoku test\xspace}
\newcommand{\torustest}{Torus Matrix Multiplication test\xspace}
\newlength{\plotwidthSMP}
\setlength{\plotwidthSMP}{0.39\textwidth}
\newlength{\plotwidthDist}
\setlength{\plotwidthDist}{0.6\textwidth}

@@

%\performanceSkelRMSM{4423}{32}

%\speedupSkelRMSM{4423}{32}

%\performanceSkelRMSM{4423}{64}

%\speedupSkelRMSM{4423}{64}

%\performanceSkelRMSM{9941}{32}

%\speedupSkelRMSM{9941}{32}{32}

%\performanceSkelRMSM{9941}{64}

%\speedupSkelRMSM{9941}{64}

%\performanceSkelRMSM{11213}{32}

% \newcommand{\performanceSkelRMDist}[4]{
% \performanceplot{Parallel run time \\ SkelRM #1 #2}{PArrows}{256}{#3}{
% \addplot table [scatter, x="nCores", y="time", col sep=comma, mark=none,
% smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-parrows-#1-#2.csv};
% % \addplot table [scatter, x="nCores", y="time", col sep=comma, mark=none,
% % smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-eden-#1-#2.csv};
% }{#4}
% }

\newcommand{\speedupSkelRMDist}[4]{
\speedupplot{Speedup of \rmtest ``#1,#2''}{PArrows}{256}{#3}{
% \addplot [mark=*,very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
% smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-parrows-11213-#2.csv};
\addplot [mark=*,very thick,blue] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-parrows-#1-#2.csv};
% \addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
% smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-eden-#1-#2.csv};
}{#4}{\plotwidthDist}
}

\newcommand{\performanceSkelRMDistDiff}[5]{
\performancediffplot{Run time differences\\for \rmtest ``#1, #2''}{(Eden $-$ PArrows)}{256}{#3}{
\addplot+[mark=*,very thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="time", y error="max stddev", col sep=comma, mark=dots,
smooth]{benchmarks/distributed-rm/#1-#2-diff.csv};
}{#4}{#5}{\plotwidthDist}
}

% \newcommand{\speedupSkelRMDistDiff}[4]{
% \speedupdiffplot{Parallel speedup difference \\ of SkelRM #1 #2}{(Eden - PArrows)}{512}{#3}{
% \addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
% smooth]{benchmarks/distributed-rm/#1-#2-diff.csv};
% }{#4}
% }

%\performanceSkelRMDist{9941}{256}{16,32,64,128,256,512}{528}

%\performanceSkelRMDistDiff{9941}{256}{16,32,64,128,256,512}{0.11}{528}

%\speedupSkelRMDist{9941}{256}{16,32,64,128,256,512}{528}

%\speedupSkelRMDistDiff{9941}{256}{16,32,64,128,256,512}{528}

%\performanceSkelRMDist{11213}{256}{16,32,64,128,256,512}{528}

%\performanceSkelRMDistDiff{11213}{256}{16,32,64,128,256,512}{0.1}{528}

%\speedupSkelRMDist{11213}{256}{16,32,64,128,256,512}{528}

%\speedupSkelRMDistDiff{11213}{256}{16,32,64,128,256,512}{528}

\newcommand{\speedupSudokuSM}[1]{
\speedupplot{Speedup of \sudokutest ``#1''}{Eden CP, Multicore, |Par| Monad}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-eden-sudoku17.#1.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-mult-sudoku17.#1.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-par-sudoku17.#1.txt.csv};
%\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
%smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parmonad-sudoku-sudoku17.#1.txt.csv};
}{17}{\plotwidthSMP}
}

%\speedupSkelRMDistDiff{44497}{256}{32,64,128,256,512}{544}

%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Text

@@

\begin{table}
\caption{The benchmarks we use in this paper.}
\label{tab:benches}
\centering
%% something was wrong with separators in table
\renewcommand{\tabcolsep}{1em}
\begin{tabular}{lccll}
\toprule
Name & Area & Type & Origin & Citation \\
\midrule
\rmtest & Mathematics & |parMap+reduce| & Eden & \citet{Lobachev2012}\\
Jacobi sum test & Mathematics & |workpool+reduce| & Eden & \citet{Lobachev2012}\\
Gentleman & Mathematics & |torus| & Eden & \citet{Eden:SkeletonBookChapter02}\\
Sudoku & Puzzle & |parMap| & |Par| Monad & \citet{par-monad} 
\tablefootnote{actual code from: http://community.haskell.org/~simonmar/par-tutorial.pdf and https://github.com/simonmar/parconc-examples}\\
\bottomrule
\end{tabular}
\end{table}

@@

\subsubsection{\rmtest}
\olcomment{THE ACTUAL TEXT IS MISSING. What do we see in the plots?
  Why is it good?}
The multicore version of our parallel \rmtest benchmark is in
Figure~\ref{fig:bench-rm-sm}. We have executed the test with 32 and 64
tasks. The plot shows the PArrows-enabled versions with corresponding backends.
The performance of PArrows/Eden~CP in shared memory is slightly better than
for SMP variants such as PArrows/Multicore Haskell and PArrows/|Par|
Monad. The reason for this behavior lies in the backend in our reasoning. One
possible explanation is garbage collection. It is easier to GC
(independently) $n$ heaps than to GC one large. This agrees with known
results\olcomment{WHICH EXACTLY?} that motivate the efforts for
parallel GC in SMP-based Haskells.

@@

>>>>

\newcommand{\rmtest}{Rabin--Miller test\xspace}
\newcommand{\sudokutest}{Sudoku solver\xspace}
\newcommand{\jacobitest}{Jacobi sum test\xsp}
\newcommand{\torustest}{Gentleman\xspace}
\newlength{\plotwidthSMP}
\setlength{\plotwidthSMP}{0.39\textwidth}
\newlength{\plotwidthDist}
\setlength{\plotwidthDist}{0.6\textwidth}

@@

@@

\begin{table}
\caption{The benchmarks we use in this paper.}
\label{tab:benches}
\centering
%% something was wrong with separators in table
\renewcommand{\tabcolsep}{1em}
\begin{tabular}{lccll}
\toprule
Name & Area & Type & Origin & Citation \\
\midrule
\rmtest & Mathematics & |parMap+reduce| & Eden & \citet{Lobachev2012}\\
\jacobitest & Mathematics & |workpool+reduce| & Eden & \citet{Lobachev2012}\\
\torustest & Mathematics & |torus| & Eden & \citet{Eden:SkeletonBookChapter02}\\
\sudokutest & Puzzle & |parMap| & |Par| Monad & \citet{par-monad} 
\tablefootnote{actual code from: http://community.haskell.org/~simonmar/par-tutorial.pdf and https://github.com/simonmar/parconc-examples}\\
\bottomrule
\end{tabular}
\end{table}

@@

\subsubsection{\rmtest}

\newcommand{\speedupSkelRMDist}[4]{
\speedupplot{Speedup of \rmtest ``#2''}{PArrows}{256}{#3}{
% \addplot [mark=*,very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
% smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-parrows-11213-#2.csv};
\addplot [mark=*,very thick,blue] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-parrows-#1-#2.csv};
% \addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
% smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-eden-#1-#2.csv};
}{#4}{\plotwidthDist}
}

\newcommand{\performanceSkelRMDistDiff}[5]{
\performancediffplot{Run time differences\\for \rmtest ``#2''}{(Eden $-$ PArrows)}{256}{#3}{
\addplot+[mark=*,very thick,error bars/.cd,
    y dir=both,y explicit] table [x="nCores", y="time", y error="max stddev", col sep=comma, mark=dots,
smooth]{benchmarks/distributed-rm/#1-#2-diff.csv};
}{#4}{#5}{\plotwidthDist}
}

\olcomment{THE ACTUAL TEXT IS MISSING. What do we see in the plots?
  Why is it good?}
The multicore version of our parallel \rmtest benchmark is in
Figure~\ref{fig:bench-rm-sm}. We have executed the test with 32 and 64
tasks. The plot shows the PArrows-enabled versions with corresponding backends.
The performance of PArrows/Eden~CP in shared memory is slightly better than
for SMP variants such as PArrows/Multicore Haskell and PArrows/|Par|
Monad. The reason for this behavior lies in the backend in our reasoning. One
possible explanation is garbage collection. It is easier to GC
(independently) $n$ heaps than to GC one large. This agrees with known
results\olcomment{WHICH EXACTLY?} that motivate the efforts for
parallel GC in SMP-based Haskells.

@@

\subsubsection{\torustest}

\subsubsection{\sudokutest}

\newcommand{\speedupSudokuSM}[1]{
\speedupplot{ \sudokutest ``#1''}{Eden CP, Multicore, |Par| Monad}{16}{4}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-eden-sudoku17.#1.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-mult-sudoku17.#1.txt.csv};
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parrows-sudoku-parmap-par-sudoku17.#1.txt.csv};
%\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
%smooth]{benchmarks/sudoku-sm/bench-sudoku-sm.bench.parmonad-sudoku-sudoku17.#1.txt.csv};
}{17}{\plotwidthSMP}
}
